<<<<<<< HEAD
\begin{thebibliography}{90}   
\rhead[\fancyplain{}{\bfseries \leftmark}]{\fancyplain{}{\bfseries
\thepage}}
\addcontentsline{toc}{chapter}{Bibliografia}


\bibitem{ISOOSIBibliography} ISO 7498-2:1989, \textit{``Information processing systems -- Open Systems Interconnection -- Basic Reference Model -- Part 2: Security Architecture''}

\bibitem{IEEE802dot11Bibliography} IEEE 802.11\textsuperscript{TM} - 2012 IEEE Standard for Information technology, \textit{``Telecommunications and information exchange between systems Local and metropolitan area networks -- Specific requirements Part 11: Wireless LAN Medium Access Control (MAC) and Physical Layer (PHY) Specifications''}

\bibitem{SecurityBibliography} A. H. Lashkari, M. M. S. Danesh, B. Samadi, \textit{``A survey on wireless security protocols (WEP, WPA and WPA2/802.11i)''}, Proc. 2nd IEEE ICCSIT, Beijing, China, Aug. 2009.

\bibitem{IPv4Bibliography} IETF RFC: 791, \textit{``Internet Protocol''}.
\bibitem{IPv6Bibliography} IETF RFC: 2460,\textit{``Internet Protocol, Version 6 (IPv6) Specification''}.
\bibitem{UDPBibliography} IETF RFC: 768, \textit{``User Datagram Protocol''}.

\bibitem{VoIPBibliography} B. Goode, \textit{``Voice Over Internet Protocol (VoIP)''}, Proceedings of the IEEE, vol.90, No.9, sept. 2002.

\bibitem{RTPBibliography} IETF RFC: 3550, \textit{``RTP: A Transport Protocol for Real-Time Applications''}.

\bibitem{Hdot323} ITU-T Recommendation H.323 \textit{``Packet-based multimedia communications systems ''}.

\bibitem{SIPBibliography} IETF RFC: 3261, \textit{``SIP: Session Initiation Protocol''}.


\bibitem{KernelLinuxChangelog} \textit{``Linux 4.0.1 ChangeLog''}, https://www.kernel.org/pub/linux/kernel/v4.x/ChangeLog-4.0.1, consultato Giugno 2015

\bibitem{SocketBufferLinuxFoundation} \textit{``The sk\_buff structure''}, http://www.linuxfoundation.org/collaborate/workgroups/networking/sk\_buff, consultato Giugno 2015


\bibitem{MobileIPv6FastHandovers} R. Koodli, \textit{``Mobile IPv6 Fast Handovers''}, IETF RFC 4068, June 2008.
\bibitem{HierarchicalMobileIPv6}  H. Soliman, C. Castelluccia, K. ElMalki, L. Bellier, \textit{``Hierarchical Mobile IPv6 (HMIPv6) Mobility Management''}, IETF RFC 5380, October 2008.
\bibitem{ProxyMobileIPv6} S.Gundavelli, K.Leung, V.Devarapalli, K. Chowdhury, B. Patil \textit{``Proxy Mobile IPv6''}, IETF RFC 5213, August 2008.
\bibitem{HostIdentityProtocol} R. Moskowitz, P. Nikander, P. Jokela, T. Henderson \textit{``Host Identity Protocol''}, IETF RFC 5201, April 2008. 
\bibitem{LIN6} F. Teraoka, \textit{``LIN6: A Solution to Multihoming and Mobility in IPv6''}, IETF Internet Draft, 2006.
\bibitem{TMSP}	T.M. Lim, Chai Kiat Yeo, Francis Bu Sung Lee, Quang Vinh Le, \textit{``TMSP: Terminal Mobility Support Protocol''}, IEEE Transactions on Mobile Computing, vol. 8, no. 6, June 2009.
\bibitem{802dot11r} IEEE Std 802.11r-2008, \textit{``Amendment 2: Fast Basic Service Set (BSS) Transition''} .
\bibitem{802dot11e} IEEE 802.11e, \textit{ Wireless LAN Medium Access Control and Physical Layer Specification: Amendment for Quality of Service Enhancements}, 2005.
\bibitem{ABPSSipBased} V. Ghini, S. Ferretti, F. Panzieri, \textit{The ``always best packet switching'' architecture for sip-based mobile multimedia services}, Journal of Systems and Software, 2011.
\bibitem{ABPSVoipCaseStudy} V. Ghini, G. Lodi, F. Panzieri, \textit{``Always Best Packet Switching: the Mobile VoIP Case Study''}, Journal of Communications, vol. 4, no. 9, October 2009.

\bibitem{CISCOLISP} \textit{``Locator/ID Separation Protocol LISP''}, http://lisp.cisco.com/lisp\_over.html, consultato Luglio 2015.

\bibitem{mac80211Bibliography} \textit{``The  mac80211 developer documentation ''} ,https://wireless.wiki.kernel.org/en/developers/documentation/mac80211, consultato Luglio 2015.
\end{thebibliography}
=======
\begin{thebibliography}{90}   
\rhead[\fancyplain{}{\bfseries \leftmark}]{\fancyplain{}{\bfseries
\thepage}}
\addcontentsline{toc}{chapter}{Bibliografia}


\bibitem{ISOOSIBibliography} ISO 7498-2:1989 https://www.iso.org/obp/ui/\#iso:std:14256:en.

\bibitem{IEEE802dot11Bibliography} IEEE 802.11\textsuperscript{TM} - 2012 IEEE Standard for Information technology--Telecommunications and information exchange between systems Local and metropolitan area networks--Specific requirements Part 11: Wireless LAN Medium Access Control (MAC) and Physical Layer (PHY) Specifications

\bibitem{SecurityBibliography} A. H. Lashkari, M. M. S. Danesh, and B. Samadi, ``A survey on wireless security protocols (WEP, WPA and WPA2/802.11i)'' in Proc. 2nd IEEE ICCSIT, Beijing, China, Aug. 2009.

\bibitem{IPv4Bibliography} IETF RFC: 791 http://www.ietf.org/rfc/rfc791.txt
\bibitem{IPv6Bibliography} IETF RFC: 2460 http://www.ietf.org/rfc/rfc2460.txt

\bibitem{UDPBibliography} IETF RFC: 768 https://www.ietf.org/rfc/rfc768.txt

\bibitem{VoIPBibliography} B. Goode,``Voice Over Internet Protocol (VoIP)'', Proceedings of the IEEE, vol.90, No.9, sept. 2002

\bibitem{RTPBibliography} IETF RFC: 3550 http://www.ietf.org/rfc/rfc3550.txt

\bibitem{Hdot323} ITU-T Recommendation H.323 (12/09)

\bibitem{SIPBibliography} IETF RFC: 3261 http://www.ietf.org/rfc/rfc3261.txt



\bibitem{KernelLinuxChangelog} https://www.kernel.org/pub/linux/kernel/v4.x/ChangeLog-4.0.1

\bibitem{SocketBufferLinuxFoundation} http://www.linuxfoundation.org/collaborate/workgroups/networking/sk\_buff


\bibitem{MobileIPv6FastHandovers} R. Koodli, ``Mobile IPv6 Fast Handovers'', IETF RFC 4068, June 2008.
\bibitem{HierarchicalMobileIPv6}  H. Soliman, C. Castelluccia, K. ElMalki, L. Bellier, ``Hierarchical Mobile IPv6 (HMIPv6) Mobility Management'', IETF RFC 5380, October 2008.
\bibitem{ProxyMobileIPv6} S.Gundavelli, K.Leung, V.Devarapalli, K. Chowdhury, B. Patil ``Proxy Mobile IPv6'', IETF RFC 5213, August 2008.
\bibitem{HostIdentityProtocol} R. Moskowitz, P. Nikander, P. Jokela, T. Henderson ``Host Identity Protocol'', IETF RFC 5201, April 2008. 
\bibitem{LIN6} F. Teraoka, ``LIN6: A Solution to Multihoming and Mobility in IPv6'', IETF Internet Draft, draft-teraoka-multi6-lin6-00.txt, 2006.
\bibitem{TMSP}	T.M. Lim, Chai Kiat Yeo, Francis Bu Sung Lee, Quang Vinh Le, ``TMSP: Terminal Mobility Support Protocol'', IEEE Transactions on Mobile Computing, vol. 8, no. 6, pp. 849-863, June 2009.
\bibitem{802dot11r} IEEE Std 802.11r-2008; ``Amendment 2: Fast Basic Service Set (BSS) Transition''; http://standards.ieee.org/getieee802/download/802.11r- 2008.pdf.
\bibitem{802dot11e} IEEE 802.11e: Wireless LAN Medium Access Control and Physical Layer Specification: Amendment for Quality of Service Enhancements. 2005.
\bibitem{ABPSSipBased} V. Ghini, S. Ferretti, and F. Panzieri. The ``always best packet switching'' architecture for sip-based mobile multimedia services. Journal of Systems and Software, 2011.
\bibitem{ABPSVoipCaseStudy} V. Ghini, G. Lodi, F. Panzieri, Always Best Packet Switching: the Mobile VoIP Case Study, Journal of Communications, vol. 4, no. 9, October 2009.
\bibitem{CISCOLISP} http://lisp.cisco.com/lisp\_over.html
\bibitem{ITUTRacc} ITU-T Recommendation G.1010, ``End-user multimedia QoS categories'', November 2001. 
\end{thebibliography}
>>>>>>> 9ccbbfe5c01c7b732d41d99e768496dc837d9f67
